%-------------------------
% Resume in Latex
% Author : Ujjwal Singh
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://ujjwalksingh.com/}{\Large Ujjwal Kumar Singh}} & Email : \href{mailto:ujjwalks01@gmail.com}{ujjwalks01@gmail.com}\\
  \href{http://ujjwalksingh.com/}{http://www.ujjwalksingh.com} & Mobile : +91 8826235246 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Indian Institute of Technology}{Kanpur, India}
      {Bachelor of Technology in Computer Science and Engineering;  CGPA: 8.2}{Aug. 2010 -- Dec. 2014}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Mindtickle}{Pune, India}
      {SDEII}{Jun 2017 - Present}
      \resumeItemListStart
        \resumeItem{Deep Link and Cross-Platform Integration}
          {Node REST microservice to generate deep link to help routing on web and on mobile.}
        \resumeItem{Augment Reality}
          {Interactive virtual content for user in real environment. Uses image processing and spatial tracking to augment real conspicuous environment.}
        \resumeItem{Mobile Architecture}
          {Architect and Developer of main customer android app.}
    
      \resumeItemListEnd

    \resumeSubheading
      {ruly}{Delhi, India}
      {Co-Founder}{Oct 2015 - Feb 2017}
      \resumeItemListStart
      	\resumeItem{Platform}
	{Social platform for individual legal needs and queries.}
        \resumeItem{Recommendations and Indexing}
          {Recommendations based on user activity and likes. Auto-suggestion for query asked based on indexing using solr and ES.}
        \resumeItem{Database}
          {Primary database - MySQL database using Amazon RDS. Document indexing using Amazon elastic search service.}
        \resumeItem{Data Collection}
          {Collected data for legal judgments, police station all over India, lawyers on social platforms.}
        \resumeItem{Content Discovery}
          {Designed platform with primary concern for relevant content discovery. Relevant Q/A's, judgments, legal project can be searched with single text query.}
        \resumeItem{Analytics}
          {Logging all user activities using kafka and gcloud big data.}
        \resumeItem{Android App}
          {Created customisable android app for lawyer and users.}
      \resumeItemListEnd

    \resumeSubheading
      {Samsung Electronics}{Noida, India}
      {Engineer}{July 2014 and Oct 2015}
      \resumeItemListStart
      \resumeItem{Ideation and Commercialisation}
          {Involves sketching and prototyping ideas for patents and developing commercial product for general public.}
        \resumeItem{RPM: Resource Power Manager}
          {RPM responsibility is to manage power supply to various components in mobile. Enhancement of battery life and monitoring power consumption}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Data-Mining Research Publication}
      {K-Dominant Skyline Join Queries: Extending the Join Paradigm to K-Dominant Skylines.}
      \resumeSubItem{Google Assisstant}
      {Custom google assistant with capabilities to book Uber cab.}
      \resumeSubItem{Slack Bot}
      {Intelligent messaging slack bot with small talk capabilities using Dialogflow.}
    \resumeSubItem{Gaming Agent}
      {Agent capable of playing expertly FSM(Finite State Machine) games described using GDL(Game Description Language).}
    \resumeSubItem{Recommendation System}
      {Movie recommender systems using collaborative filtering on MovieLens datasets.}
    \resumeSubItem{Hostel Management System}
      {Django based application to manage hall (alias for Hostel in IITK).}
  \resumeSubHeadingListEnd
  
        %--------ACHIEVEMENTS------------
\section{Achievements}
   \resumeSubHeadingListStart
     \resumeSubItem{Data Engineering Publication in IEEE Conference}
     {\href{https://ieeexplore.ieee.org/document/7929945/}{K-Dominant Skyline Join Queries: Extending the Join Paradigm to K-Dominant Skylines}}
     \resumeSubItem{ACM ICPC International Collegiate Programming Contest 2012}
     {Kanpur site regional finalist}
  
  \resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
  \resumeSubHeadingListStart
    \item{
      \textbf{Languages}{: Kotlin, Python, JS, SQL, Java, Scala}
      \hfill
      \textbf{Technologies}{: AWS, Kafka, Docker, Android, Django}
    }
  \resumeSubHeadingListEnd
  
  %--------HOBBIES------------
\section{Hobbies}
  \begin{description}
    \item{
     {Reading non-fictional books, \href{https://medium.com/@ujjwal.singh}{Tech Blogger}, Gamer}
   }
    \end{description}


%-------------------------------------------
\end{document}
